Models of gravitational lens candidates from Space Warps CFHTLS

### 2017-11-21 KuengR__Lens_models.tex
cleanup: names

\begin{abstract}
We report modelling follow-up of recently-discovered
gravitational-lens candidates in the Canada France Hawaii Telescope
Legacy Survey. Lens modelling was done by a small group of
specially-interested volunteers from the \SW citizen-science community
who originally found the candidate lenses.  Models are categorised
according to seven diagnostics indicating (a)~the image morphology and
how clear or indistinct it is, (b)~whether the mass map and synthetic
lensed image appear to be plausible, and (c)~how the lens-model mass
compares with the stellar mass and the abundance-matched halo mass.
The lensing masses range from $\sim10^{11}M_\odot$ to
$>10^{13}M_\odot$. Preliminary estimates of the stellar masses show a
smaller spread in stellar mass (except for two lenses): a factor of a
few below or above $\sim10^{11}M_\odot$.  Therefore, we expect the
stellar-to-total mass fraction to decline sharply as lensing mass
increases.  The most massive system with a convincing model is
J1434+522 (\sw{05}).  The two low-mass outliers are J0206-095
(\sw{19}) and J2217+015 (\sw{42}); if these two are indeed lenses,
they probe an interesting regime of very low star-formation
efficiency.  Some improvements to the modelling software
(SpaghettiLens), and discussion of strategies regarding scaling to
future surveys with more and frequent discoveries, are included.
\end{abstract}

>>>>

\begin{abstract}
We report modelling follow-up of recently-discovered
gravitational-lens candidates in the Canada France Hawaii Telescope
Legacy Survey. Lens modelling was done by a small group of
specially-interested volunteers from the \SW citizen-science community
who originally found the candidate lenses.  Models are categorised
according to seven diagnostics indicating (a)~the image morphology and
how clear or indistinct it is, (b)~whether the mass map and synthetic
lensed image appear to be plausible, and (c)~how the lens-model mass
compares with the stellar mass and the abundance-matched halo mass.
The lensing masses range from $\sim10^{11}M_\odot$ to
$>10^{13}M_\odot$. Preliminary estimates of the stellar masses show a
smaller spread in stellar mass (except for two lenses): a factor of a
few below or above $\sim10^{11}M_\odot$.  Therefore, we expect the
stellar-to-total mass fraction to decline sharply as lensing mass
increases.  The most massive system with a convincing model is
J1434+522 (\sw{05}).  The two low-mass outliers are J0206$-$095
(\sw{19}) and J2217+015 (\sw{42}); if these two are indeed lenses,
they probe an interesting regime of very low star-formation
efficiency.  Some improvements to the modelling software
(SpaghettiLens), and discussion of strategies regarding scaling to
future surveys with more and frequent discoveries, are included.
\end{abstract}
